Faithful Variable Screening for\\ High-Dimensional Convex Regression

### 2015-04-27 tex/scam/reviews-v1/response-v1.tex

\documentclass[pdftex,12pt]{article}

\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{enumerate}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
\usepackage{graphicx,subfigure}
\usepackage[pdftex]{color}
\usepackage{epic,eepic,eepicemu}
\usepackage{epsf}
\usepackage{epsfig}
\usepackage{fancyhdr}
\usepackage{graphics}
\usepackage{psfrag,latexsym}
\usepackage{times}
\newcommand{\thetamin}{\ensuremath{\theta^*_{min}}}
\newcommand{\mutinc}{\ensuremath{\alpha}}
\bibliographystyle{abbrv}

\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-6cm}
\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-4cm}
\addtolength{\textheight}{-1.1\headheight}
\addtolength{\textheight}{-\headsep}
\addtolength{\textheight}{-\footskip}
\setlength{\oddsidemargin}{0.5cm}
\setlength{\evensidemargin}{0.5cm}
\def\P{{\mathbb P}}
\def\E{{\mathbb E}}
\def\degmax{d}
\def\pdim{p}
\def\numobs{n}
\let\hat\widehat
\definecolor{blue}{rgb}{0.01,0.01,0.75}
\def\reviewercomment#1{{\it\textcolor{blue}{#1}}\smallskip}
\parindent0pt
\parskip12pt

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\vspace*{5pt}

We thank the reviewers for their helpful comments regarding our
submission. We have carefully addressed all these comments. The
following describes the revisions made to the manuscript in response
to the reviews.

\subsection*{Associate Editor}

\reviewercomment{Below I recapitulate a few
point of the reviewers', along with some questions/comments of my own.
These (as well as other points in the reviews) need to be thoroughly
addressed in the revised manuscript.}

\begin{enumerate}
\item \reviewercomment{Boundary flatness condition: much of the paper's analysis hinges on
this condition.  Reviewer 3 raises some concerns about when it holds,
especially for functions that are not necessarily supported on the
unit hypercube.  See also the point below.}

We have added commentary on this here and here.

\item \reviewercomment{Intuitively, variable selection is very closely related to
estimating a function (or possibly its partial derivatives) in the
sup-norm.  It is well-known that accurate estimation of functions
(whether in $L^2$ or the sup-norm) with bounded smoothness in dimension
$s$ requires a sample size that grows exponentially in $s$.  For this
reason, the past result of Comminges and Dalalyan (suggesting an
exponential growth for variable selection) is to be expected.
However, in terms of metric entropy, the class of convex functions
behaves roughly like the class of two-smooth functions (e.g., Dryanov
(2009)).  So at first glance, this makes the result of this paper
rather surprising---namely, that one can somehow side-step any
exponential growth in $s$, even though the metric entropy is still
scaling as badly as the case of 2-smooth functions.  I wondered if the
authors could comment and shed insight on this fact, which seems a
little counterintuitive.  What I suspect that it could mean is that
the additive faithfulness (AF) condition, or one of the sufficient
conditions for AF (namely boundary flatness) are somehow very
restrictive.  Could the authors comment on these issues?}

We have made these revisions.

\item \reviewercomment{Writing and proofs need to be tidied up in places to make it easier
to follow.  See various comments of referees, particularly the
detailed ones of R2.  Also, in Theorem 3, please remind the author of
when/where the AC/DC estimators were defined.  (I was forced to dig
back through.)}

We have tidied up.

\end{enumerate}

\subsection*{Reviewer 1}

\reviewercomment{Conceptually, I have a few questions for the authors to address:}

\begin{enumerate}[(1)]
\item \reviewercomment{If the true regression function $f_0$ can actually be written as a
sum of univariate convex functions (plus noise), are there natural
conditions that one can provide for when additive faithfulness will
hold? Similarly, is there a simpler version of Theorem 3 that can be
stated when $f_0$ is actually a sum of univariate convex functions? This
would seem to depend on an appropriate statement for Assumption (A3).}

\item \reviewercomment{If we actually wish to fit smooth convex univariate components, is
it easy to add this condition as a regularization term and incorporate
it into the analysis?}

\item \reviewercomment{Assuming model selection consistency, can one derive prediction
error bounds using the fitted $f_k$'s and $g_k$'s, as well? Prediction error
bounds seem quite relevant due to possible model misspecification when
$f_0$ is not actually a sum of univariate convex functions.}

\item \reviewercomment{In order to improve clarity, the authors should define the convex
additive model at the top of page 5: $f(x_i) = \sum_{k=1}^p f_k(x_{ik})$, where the
$f_k$'s are convex.  Otherwise, the notation in equation (2.3) is
initially a bit confusing.}

\item \reviewercomment{Another notational comment: the use of the
distribution function $F$ seems unnecessary (e.g., Lemma 3.1 and
Corollary 3.1), since everything is already defined in terms of the
joint density function $p(x)$. (An additional suggestion would be to use
a different letter to represent the joint density function, since $p$ is
already used to represent the dimensionality of the distribution.)}

\item \reviewercomment{I would suggest including the dependence on the positive-valued lower
bound on $p(x)$ (as assumed in (A5)) in the statement of Theorem 3. This
is a point worth commenting upon, since the earlier theorems only
require $p(x)$ to be strictly positive. Assumption (A5) seems like it
could also be interpreted as a sort of minimum signal strength
requirement for successful variable selection.}

\item \reviewercomment{It would be good to point to Assumption (A3) at the beginning of
Section 5 when discussing the $B$-boundedness condition. In the third
paragraph, the authors might note that the $B$-boundedness condition
arises from the analysis of Theorem 5.2. To clarify, the penultimate
paragraph on page 22 should state that Theorem 5.1 controls false
positives alone, whereas Theorem 5.3 (to follow) provides
finite-sample results controlling the false negative rate.}

\item \reviewercomment{At the top
of page 23, the remark regarding mutual incoherence conditions is a
bit confusing. Aren’t the conditions imposed in Theorem 5.1 on the
covariates essentially analogous to the mutual incoherence conditions
in this case? }

\item \reviewercomment{In the simulation section, the authors might consider comparing the
set of variables selected after the AC step only with the set of
variables selected via the entire AC/DC algorithm. This would help
illustrate the necessity of the concave fitting step in addition to
the convex additive fit alone.}

Minor typos:
\begin{enumerate}[(i)]
\item \reviewercomment{In Section 2.3, it would be good to actually state the regularized
objective function being analyzed, rather than waiting until Section
4.}
\item \reviewercomment{Assumption (A3) on page 7 is missing the subscript $\infty$.}
\item \reviewercomment{The parameter $\sigma$ is never defined in Section 2.3. Reading ahead,
it seems to be the sub-Gaussian parameter of the additive noise.}
\item \reviewercomment{Perhaps Section 3 should be titled something other than ``Additive
faithfulness'' (maybe ``Population- level results''?).}
\item \reviewercomment{The first paragraph of Section 5 should read
  ``Figure 3'' rather than ``Algorithm 3.''}

\item \reviewercomment{The second paragraph of Section 5 has $m\hat{}u$ instead of $\hat\mu$.}
\item \reviewercomment{The first sentence of Section 5.1 should read optimization (4.8).}
\end{enumerate}

\end{enumerate}

\subsection*{Reviewer 2}

\reviewercomment{I found many (unimportant) mistakes in the proofs (I
  did not mention them all in the minor comments), which need to be
  read again carefully.}

\begin{enumerate}
\item \reviewercomment{I have a problem with the assertion of
  uniqueness in Lemma 3.1 and Therorem 3.2. First, in Lemma 3.1, it is
  clear that $f^∗$ is unique. But $(f_1^∗, \ldots, f_p^∗)$ is not. What is
  shown is that, for $k$ fixed and given $(f_j^*)_{j\neq k}$, $f_k^*$ is unique. Next,
  in Theorem 3.2, the proof of uniqueness (bottom of page 16 and top
  of page 17) is not at all correct.
   Now, to see why I think that, with the assumtions made on $X$, there is
   not uniqueness, simply suppose for instance that $p = 2$ and $X_2 = g(X_1)$
   for a certain function $g$. Then if $(f_1^∗, f_2^∗)$ is a solution,
   $(f_1^∗ + f_2^ \circ g, 0)$ is also a solution.}

\end{enumerate}

\subsection*{Reviewer 3}

Major comments:

\begin{enumerate}
\item \reviewercomment{The basis of all the results seem to be the boundary flatness
condition. This condition seems to be an artifact of the analysis and
based on my reading, it is unclear how restrctive this assumption
is. The authors claim it is weak just after stating it and then
present several straightforward examples in which it doesn't hold
(e.g. $f(x_1,x_2)=x_1 x_2$) and multivariate Gaussian examples. Hence it is unclear to me how
likely a given function is likely to fit into this framework.}

\item \reviewercomment{Following on from the previous point, the simulation study also does
not add any further insight to this issue since the simulations are
for multivariate Gaussians where other parametric approaches that deal
with covariance seem more suitable. It is puzzling to me that the
authors did not consider non-parametric examples where the additive
model framework seems more suitable.}

\end{enumerate}

Minor comments:

\begin{enumerate}
\item \reviewercomment{I didn't think there was any need for Section 2
  since it feels very repetitive and slightly confusing that parts of
  the text are repeated almost verbatim. I would suggest removing this section.}

\item \reviewercomment{Page 2, second last paragraph `and and.'}
\end{enumerate}

\vspace*{10pt}

Sincerely,

Min Xu, Minhua Chen, and John Lafferty\\[1pt]
\today{}

\bibliography{local}
\end{document}

### 2015-04-27 tex/scam/supplement.tex
appendix edits

To check that other rows of stationarity condition holds, we characterize $[\frac{1}{n} \Delta_k^\tran \hat{r}]_j$:
\begin{align*}
[\frac{1}{n} \Delta_k^\tran \hat{r}]_j &= \frac{1}{n} \sum_{i > j} (X_{ik} - X_{jk}) \hat{r}_i \\
  & = \frac{1}{n} \sum_{i > j} \sum_{j < i' \leq i} \mathsf{gap}_{i'} \hat{r}_i \\
 & = \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \sum_{i \geq i'} \hat{r}_i \\
 & = \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \mathbf{1}_{i':n}^\tran \hat{r} 
\end{align*}
where we denote $\mathsf{gap}_{i'} = X_{i'k} - X_{(i'-1)k}$.

@@

We know $\frac{1}{n} \Delta_k^\tran \hat{r}$ and $\lambda \Delta_k^\tran \mathbf{u}$ are equal in the first coordinate. We will show that the second sequence increases faster than the first sequence which will imply that the second sequence is larger than the first in the first half of the coordinates. We will then work similarly but backwards for the second half.

Following our strategy, We first compare $[\lambda \Delta_k^\tran \mathbf{u}]_j$ and $[\frac{1}{n} \Delta_k^\tran \hat{r}]_j$ for $j=1,..., i^*-1$.

@@

We now prove that if $\{ \hat{d}'_k \}_{k = 1,..., p}$ is another
solution, then it must be that $\hat{d}'_k = 0$ for all $k \in S^c$ as
well.  We first claim that $\sum_{k=1}^p \bar{\Delta}_k \hat{d}_k =
\sum_{k=1}^p \bar{\Delta}_k \hat{d}'_k$. If this were not true, then a
convex combination of $\hat{d}_k, \hat{d}'_k$ would achieve a strictly
lower objective on the quadratic term. More precisely, let $\zeta \in
[0,1]$. If $\sum_{k=1}^p \bar{\Delta}_k \hat{d}'_k \neq \sum_{k=1}^p
\bar{\Delta}_k \hat{d}_k$, then $\| Y - \sum_{k=1}^p \bar{\Delta}_k
\big( \hat{d}_k + \zeta ( \hat{d}'_k - \hat{d}_k) \big) \|_2^2$ is
strongly convex as a function of $\nu$. Thus, it cannot be that
$\hat{d}_k$ and $\hat{d}'_k$ both achieve optimal objective, and we
have reached a contradiction.

Now, we look at the stationarity condition for both $\{ \hat{d}_k \}$
and $\{ \hat{d}'_k \}$. Let $\mathbf{u}_k \in \partial \|
\bar{\Delta}_k \hat{d}_k \|_\infty$ and let $\mathbf{u}'_k
\in \partial \| \bar{\Delta}_k \hat{d}'_k \|_\infty$ be the two sets
of subgradients. Let $\{ \nu_{ki} \}$ and $\{
\nu'_{ki} \}$ be the two sets of positivity dual
variables, for $k=1,..,p$ and $i=1,...n-1$.  Note that since there is no positivity constraint on
$d_{k1}$, we let $\nu_{k1} = 0$ always.

@@

Since both solutions $(\hat{d}, \mathbf{u}, \nu)$ and $(\hat{d}',
\mathbf{u}', \nu')$ must satisfy the stationarity condition, we have
that
\[
\bar{\Delta}^\tran ( Y - \bar{\Delta} \hat{d} ) 
   + \lambda \sum_{k=1}^p \bar{\Delta}_k^\tran \mathbf{u}_k - \nu = 
\bar{\Delta}^\tran ( Y - \bar{\Delta} \hat{d}' ) 
   + \lambda \sum_{k=1}^p \bar{\Delta}_k^\tran \mathbf{u}'_k - \nu' = 0.
\] 
Multiplying both sides of the above equation by $\hat{d}'$,
\[
\hat{d}'^{\tran}  \bar{\Delta}^\tran ( Y - \bar{\Delta} \hat{d} ) 
    + \lambda \sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}_k - \hat{d}'^\tran \nu = \hat{d}'^{\tran}  \bar{\Delta}^\tran ( Y - \bar{\Delta} \hat{d}' ) 
    + \lambda \sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}'_k - \hat{d}'^\tran \nu'.
\]
Since $\bar{\Delta} \hat{d}_k = \bar{\Delta} \hat{d}$, $\hat{d}'^\tran \nu' = 0$ (complementary slackness), and $\hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}'_k  = \| \hat{f}'_k \|_\infty$ (where $\hat{f}'_k = \bar{\Delta}_k \hat{d}'_k$), we have that
\[
\lambda \sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}_k - \hat{d}'^\tran \nu = \lambda \sum_{k=1}^p \| \hat{f}'_k \|_\infty.
\]
On one hand, $\hat{d}'$ is a feasible solution so $\hat{d}'^\tran \nu \geq 0$ and so 
\[
\sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}_k \geq \sum_{k=1}^p \| \hat{f}'_k \|_\infty .
\]
On the other hand, by H\"older's inequality,
\begin{align*}
\sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}_k &\leq 
   \sum_{k=1}^p \| \hat{f}'_k \|_\infty \|\mathbf{u}_k \|_1 .
\end{align*}
Since $\mathbf{u}_k$ can be chosen so that $\| \mathbf{u}_k \|_1 < 1$ for all $k \in S^c$, we would get a contradiction if $\| \hat{f}'_k \|_\infty > 0$ for some $k \in S^c$. We thus conclude that $\hat{d}'$ must follow the same sparsity pattern.

The second item in the theorem concerning optimization~\ref{opt:alternate_opt_concave} is proven in exactly the same way. 
The Lagrangian of optimization~\ref{opt:alternate_opt_concave} is
\[
\mathcal{L}_{\trm{cave}}(d_k, \nu_k) = 
  \frac{1}{2n} \big\| \hat{r} - \bar{\Delta}_k d_k \big \|_2^2 + 
  \lambda \| \bar{\Delta}_k d_k \|_\infty + \sum_{k=1}^p \sum_{i=2}^{n-1} \nu_{ki} d_{ki}.
\]
with $\nu_{ki} \geq 0$.
The same reasoning applies to show that $\hat{d}_k = 0$ satisfies KKT conditions sufficient for optimality.
\end{proof}

@@

\begin{theorem} 
Suppose assumptions A1-A5 hold. Define $\tilde{\sigma} \equiv \max(\sigma, B)$. Suppose that $p \leq O\big( \exp( c n) \big)$ and $n \geq C$ for some constants $0<c<1$ and $C$. Define $\mathsf{range}_k = X_{k\pi_k(n)} - X_{k\pi_k(1)}$.

If $\lambda_n \geq 2 (8 \cdot 32) s \tilde{\sigma}  \sqrt{ \frac{1}{n} \log^2 np}$ then, with probability at least $ 1 - \frac{24}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$
\begin{align*}
& \lambda_n > \mathsf{range}_k \Big| \frac{32}{n}\hat{r}^\tran \mathbf{1}_{\pi_k(i':n)} \Big|  
\end{align*}
and $\max_{i'} \frac{X_{k\pi_k(i'+1)} - X_{k \pi_k(i')}}{\mathsf{range}_k} \leq \frac{1}{16}$ and $\mathsf{range}_k \geq 1$.

@@

Putting these observations together,
%and take another union bound across all $j$ and all $i'$:
\begin{align}
\| \hat{r} \|_\infty &\leq 2sB + \sigma \sqrt{ 2\log \frac{2n}{\delta}}) \nonumber \\
      &\leq 4 s \tilde{\sigma} \sqrt{\log \frac{2n}{\delta}} \label{eqn:stepone_rhat}
\end{align}
with probability at least $1 - \delta$, where we have defined
$\tilde{\sigma} = \max(\sigma, B)$,
and assumed that $\sqrt{\log \frac{2np}{\delta}} \geq 1$. This assumption holds under the conditions in the theorem which state that $p \leq \exp( c n)$ and $n \geq C$ for some small constant $c$ and large constant $C$.

@@

\vskip5pt
\textbf{Step 3}: {\it Apply Serfling's theorem.}  
For any $k \in S^c$, Serfling's theorem states that with probability at least $1 - \delta$
\begin{align*}
\Big
|\frac{1}{n} \hat{r}^\tran \mathbf{1}_{\pi_k(i':n)}\Big| \leq
   2\| \hat{r} \|_\infty \sqrt{ \frac{1}{n} \log \frac{2}{\delta}} + 
   \Big|\frac{1}{n} \hat{r}^\tran \mathbf{1} \Big|
\end{align*}
We need Serfling's theorem to hold for all $k = 1,...,p$ and $i' =
1,...,n$. We also need the events that $\|\hat{r}\|_\infty$ and $|
\frac{1}{n} \hat{r}^\tran \mathbf{1}|$ are small to hold. Using a
union bound, with probability at least $1-\delta$, for all $k,i'$,
\begin{align*}
\Big
|\frac{1}{n} \hat{r}^\tran \mathbf{1}_{\pi_k(i':n)}\Big| &\leq
   2\| \hat{r} \|_\infty \sqrt{ \frac{1}{n} \log \frac{6np}{\delta}} + 
   \Big|\frac{1}{n} \hat{r}^\tran \mathbf{1} \Big|\\
  &\leq 4s\tilde{\sigma}\sqrt{\log \frac{6n}{\delta}} \sqrt{\frac{1}{n}\log \frac{6np}{\delta}} + 4 s \tilde{\sigma} \sqrt{\frac{1}{n}\log \frac{12}{\delta}} \\
  &\leq 8 s\tilde{\sigma} \sqrt{ \frac{1}{n} \log^2 \frac{12np}{\delta}}
\end{align*}
In the second inequality, we used equation~\eqref{eqn:stepone_rhat}
and equation~\eqref{eqn:steptwo_rhat} from steps 1 and 2
respectively. Setting $\delta = \frac{12}{n}$ gives the desired expression.

Finally, we note that $2 \geq (X_{k\pi_k(n)} - X_{k\pi_k(1)})$ since $X_k \subset [-1,1]$. This concludes the proof for the first part of the theorem.

@@

Define $\mathsf{gap}_i = X_{k \pi_k(i+1)} - X_{k \pi_k(i)}$ for $i=1,...,n-1$ and define $\mathsf{gap}_0 = X_{k \pi_k(1)} - (-1)$ and $\mathsf{gap}_{n} = 1 - X_{k\pi_k(n)}$.

@@

\[
\frac{X_{k\pi_k(i+1)} - X_{k \pi_k(i)}}{\mathsf{range}_k} \geq 
\frac{ 1/16 }{ 2 - 1/8} \geq 1/16
\]

Taking an union bound for each $k \in S^c$, the probability of that all $\mathcal{E}_k$ hold is at least $1 - p 64 \left( 1 - \frac{1}{32} c_l \right)^n$.

$p64 \left( 1 - \frac{1}{32} c_l \right)^n = 64 p \exp( - c' n)$ for some positive constants $0< c' < 1$ dependent on $c_l$. Therefore, if $p \leq exp( c n)$ for some $0<c < c'$ and if $n$ is larger than some constant $C$, $64 p \exp( - c' n) \leq 64 \exp( - (c' - c'') n) \leq \frac{12}{n}$.

Taking an union bound with the event that $\lambda_n$ upper bounds the partial sums of $\hat{r}$ and we establish the claim.

@@

\begin{theorem}
\label{thm:convex_consistent}
Let $\tilde{\sigma} \equiv \max(\sigma, B)$, and let $\hat{f}$ be the
minimizer of the restricted regression with $\lambda \leq 512 s
\tilde{\sigma} \sqrt{ \frac{1}{n} \log^2 np}$.
Suppose $n \geq c_1 s \sqrt{sB}$.
Then with probability at least $1-\frac{C}{n}$,
\begin{align}
\|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
&\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 np},
\end{align}
where $c_1$ is an absolute constant and $c, C$ are constants possibly dependent on $b$.
\end{theorem}

@@

A sub-exponential random is the square of a sub-Gaussian random
variable \cite{vershynin2010introduction}.

>>>>

To check that $\lambda [ \Delta_k^\tran \mathbf{u} ]_j \geq [ \frac{1}{n} \Delta_k^\tran \hat{r}]_j$ for $j > 1$, we first characterize $[\frac{1}{n} \Delta_k^\tran \hat{r}]_j$:
\begin{align*}
[\frac{1}{n} \Delta_k^\tran \hat{r}]_j &= \frac{1}{n} \sum_{i > j} (X_{ik} - X_{jk}) \hat{r}_i \\
  & = \frac{1}{n} \sum_{i > j} \sum_{j < i' \leq i} \mathsf{gap}_{i'} \hat{r}_i \\
 & = \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \sum_{i \geq i'} \hat{r}_i \\
 & = \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \mathbf{1}_{i':n}^\tran \hat{r} 
\end{align*}
where we denote $\mathsf{gap}_{i'} = X_{i'k} - X_{(i'-1)k}$.

@@

We know $\frac{1}{n} \Delta_k^\tran \hat{r}$ and $\lambda \Delta_k^\tran \mathbf{u}$ are equal in the first coordinate. We will show that the second sequence increases faster than the first sequence, which will imply that the second sequence is larger than the first in the first half of the coordinates. We will then work similarly but backwards for the second half.

Following our strategy, we first compare $[\lambda \Delta_k^\tran \mathbf{u}]_j$ and $[\frac{1}{n} \Delta_k^\tran \hat{r}]_j$ for $j=1,..., i^*-1$.

@@

We now prove that if $\{ \hat{d}'_k \}_{k = 1,..., p}$ is another
solution, then it must be that $\hat{d}'_k = 0$ for all $k \in S^c$ as
well.  We first claim that $\sum_{k=1}^p \bar{\Delta}_k \hat{d}_k =
\sum_{k=1}^p \bar{\Delta}_k \hat{d}'_k$. If this were not true, then a
convex combination of $\hat{d}_k, \hat{d}'_k$ would achieve a strictly
lower objective on the quadratic term. More precisely, let $\zeta \in
[0,1]$. If $\sum_{k=1}^p \bar{\Delta}_k \hat{d}'_k \neq \sum_{k=1}^p
\bar{\Delta}_k \hat{d}_k$, then $\| Y - \sum_{k=1}^p \bar{\Delta}_k
\big( \hat{d}_k + \zeta ( \hat{d}'_k - \hat{d}_k) \big) \|_2^2$ is
strongly convex as a function of $\zeta$. Thus, it cannot be that
$\hat{d}_k$ and $\hat{d}'_k$ both achieve optimal objective, and we
have reached a contradiction.

Now, we look at the stationarity condition for both $\{ \hat{d}_k \}$
and $\{ \hat{d}'_k \}$. Let $\mathbf{u}_k \in \partial \|
\bar{\Delta}_k \hat{d}_k \|_\infty$ and let $\mathbf{u}'_k
\in \partial \| \bar{\Delta}_k \hat{d}'_k \|_\infty$ be the two sets
of subgradients. Let $\{ \nu_{ik} \}$ and $\{
\nu'_{ik} \}$ be the two sets of positivity dual
variables, for $k=1,..,p$ and $i=1,...n-1$.  Note that since there is no positivity constraint on
$d_{1k}$, we let $\nu_{1k} = 0$ always.

@@

Since both solutions $(\hat{d}, \mathbf{u}, \nu)$ and $(\hat{d}',
\mathbf{u}', \nu')$ must satisfy the stationarity condition, we have
that
\[
\bar{\Delta}^\tran ( Y - \bar{\Delta} \hat{d} ) 
   + \lambda \left( \begin{array}{c} 
          \bar{\Delta}_1^\tran \mathbf{u}_1  
          \\ ... \\ \bar{\Delta}_p^\tran \mathbf{u}_p \end{array} \right)
    - \nu = 
\bar{\Delta}^\tran ( Y - \bar{\Delta} \hat{d}' ) 
   + \lambda \left( \begin{array}{c} 
          \bar{\Delta}_1^\tran \mathbf{u}'_1  
          \\ ... \\ \bar{\Delta}_p^\tran \mathbf{u}'_p \end{array} \right)
 - \nu' = 0.
\] 
Multiplying both sides of the above equation by $\hat{d}'$,
\[
\hat{d}'^{\tran}  \bar{\Delta}^\tran ( Y - \bar{\Delta} \hat{d} ) 
    + \lambda \sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}_k - \hat{d}'^\tran \nu = \hat{d}'^{\tran}  \bar{\Delta}^\tran ( Y - \bar{\Delta} \hat{d}' ) 
    + \lambda \sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}'_k - \hat{d}'^\tran \nu'.
\]
Since $\bar{\Delta} \hat{d}' = \bar{\Delta} \hat{d}$, $\hat{d}'^\tran \nu' = 0$ (complementary slackness), and $\hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}'_k  = \| \hat{f}'_k \|_\infty$ (where $\hat{f}'_k = \bar{\Delta}_k \hat{d}'_k$), we have that
\[
\lambda \sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}_k - \hat{d}'^\tran \nu = \lambda \sum_{k=1}^p \| \hat{f}'_k \|_\infty.
\]
On one hand, $\hat{d}'$ is a feasible solution so $\hat{d}'^\tran \nu \geq 0$ and so 
\[
\sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}_k \geq \sum_{k=1}^p \| \hat{f}'_k \|_\infty .
\]
On the other hand, by H\"older's inequality,
\begin{align*}
\sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}_k &\leq 
   \sum_{k=1}^p \| \hat{f}'_k \|_\infty \|\mathbf{u}_k \|_1 .
\end{align*}
Since $\mathbf{u}_k$ can be chosen so that $\| \mathbf{u}_k \|_1 < 1$ for all $k \in S^c$, we would get a contradiction if $\| \hat{f}'_k \|_\infty > 0$ for some $k \in S^c$. We thus conclude that $\hat{d}'$ must follow the same sparsity pattern.

The second item in the theorem concerning optimization~\ref{opt:alternate_opt_concave} is proven in exactly the same way. 
The Lagrangian of optimization~\ref{opt:alternate_opt_concave} is
\[
\mathcal{L}_{\trm{cave}}(c_k, \nu_k) = 
  \frac{1}{2n} \big\| \hat{r} - \bar{\Delta}_k c_k \big \|_2^2 + 
  \lambda \| \bar{\Delta}_k c_k \|_\infty + \sum_{k=1}^p \sum_{i=2}^{n-1} \nu_{ik} c_{ik}.
\]
with $\nu_{ik} \geq 0$.
The same reasoning applies to show that $\hat{c}_k = 0$ for all $k\in S^c$ satisfies KKT conditions sufficient for optimality.
\end{proof}

@@

\begin{theorem} 
Suppose assumptions A1-A5 hold. Define $\tilde{\sigma} \equiv \max(\sigma, B)$. Suppose that $p \leq O\big( \exp( c n) \big)$ and $n \geq C$ for some constants $0<c<1$ and $C$. Define $\mathsf{range}_k = X_{\pi_k(n)k} - X_{\pi_k(1)k}$.

If $\lambda_n \geq 2 (12 \cdot 32) s \tilde{\sigma}  \sqrt{ \frac{1}{n} \log^2 np}$ then, with probability at least $ 1 - \frac{24}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$
\begin{align*}
& \lambda_n > \mathsf{range}_k \Big| \frac{32}{n}\hat{r}^\tran \mathbf{1}_{\pi_k(i':n)} \Big|  
\end{align*}
and $\max_{i'} \frac{X_{\pi_k(i'+1)k} - X_{\pi_k(i')k}}{\mathsf{range}_k} \leq \frac{1}{16}$ and $\mathsf{range}_k \geq 1$.

@@

Putting these observations together,
%and take another union bound across all $j$ and all $i'$:
\begin{align}
\| \hat{r} \|_\infty &\leq 2sB + \sigma \sqrt{ 2\log \frac{2n}{\delta}}) \nonumber \\
      &\leq 4 s \tilde{\sigma} \sqrt{\log \frac{2n}{\delta}} \label{eqn:stepone_rhat}
\end{align}
with probability at least $1 - \delta$, where we have defined
$\tilde{\sigma} = \max(\sigma, B)$,
and assumed that $\sqrt{\log \frac{2n}{\delta}} \geq 1$. We will eventually take $\delta = O(1/n)$ so this assumption holds under the condition in the theorem which state that $n \geq C$ for some large constant $C$.

@@

\vskip5pt
\textbf{Step 3}: {\it Apply Serfling's theorem.}  
For any $k \in S^c$, Serfling's theorem states that with probability at least $1 - \delta$
\begin{align*}
\Big
|\frac{1}{n} \hat{r}^\tran \mathbf{1}_{\pi_k(i':n)}\Big| \leq
   2\| \hat{r} \|_\infty \sqrt{ \frac{1}{n} \log \frac{2}{\delta}} + 
   \Big|\frac{1}{n} \hat{r}^\tran \mathbf{1} \Big|
\end{align*}
We need Serfling's theorem to hold for all $k = 1,...,p$ and $i' =
1,...,n$. We also need the events that $\|\hat{r}\|_\infty$ and $|
\frac{1}{n} \hat{r}^\tran \mathbf{1}|$ are small to hold. Using a
union bound, with probability at least $1-\delta$, for all $k,i'$,
\begin{align*}
\Big
|\frac{1}{n} \hat{r}^\tran \mathbf{1}_{\pi_k(i':n)}\Big| &\leq
   2\| \hat{r} \|_\infty \sqrt{ \frac{1}{n} \log \frac{6np}{\delta}} + 
   \Big|\frac{1}{n} \hat{r}^\tran \mathbf{1} \Big|\\
  &\leq 8 s\tilde{\sigma}\sqrt{\log \frac{6n}{\delta}} \sqrt{\frac{1}{n}\log \frac{6np}{\delta}} + 4 s \tilde{\sigma} \sqrt{\frac{1}{n}\log \frac{12}{\delta}} \\
  &\leq 12 s\tilde{\sigma} \sqrt{ \frac{1}{n} \log^2 \frac{12np}{\delta}}
\end{align*}
In the second inequality, we used equation~\eqref{eqn:stepone_rhat}
and equation~\eqref{eqn:steptwo_rhat} from steps 1 and 2
respectively. Setting $\delta = \frac{12}{n}$ gives the desired expression.

Finally, we note that $2 \geq (X_{\pi_k(n)k} - X_{\pi_k(1)k})$ since $X_k \subset [-1,1]$. This concludes the proof for the first part of the theorem.

@@

Define $\mathsf{gap}_i = X_{\pi_k(i+1)k} - X_{\pi_k(i)k}$ for $i=1,...,n-1$ and define $\mathsf{gap}_0 = X_{\pi_k(1)k} - (-1)$ and $\mathsf{gap}_{n} = 1 - X_{\pi_k(n)k}$.

@@

\[
\frac{X_{k\pi_k(i+1)} - X_{k \pi_k(i)}}{\mathsf{range}_k} \leq 
\frac{ 1/16 }{ 2 - 1/8} \leq 1/16
\]

Taking a union bound for each $k \in S^c$, the probability of that all $\mathcal{E}_k$ hold is at least $1 - p 64 \left( 1 - \frac{1}{32} c_l \right)^n$.

$p64 \left( 1 - \frac{1}{32} c_l \right)^n = 64 p \exp( - c' n)$ for some positive constants $0< c' < 1$ dependent on $c_l$. Therefore, if $p \leq exp( c n)$ for some $0<c < c'$ and if $n$ is larger than some constant $C$, $64 p \exp( - c' n) \leq 64 \exp( - (c' - c) n) \leq \frac{12}{n}$.

Taking a union bound with the event that $\lambda_n$ upper bounds the partial sums of $\hat{r}$ and we establish the claim.

@@

\begin{theorem}
\label{thm:convex_consistent}
Let $\tilde{\sigma} \equiv \max(\sigma, B)$, and let $\hat{f}$ be the
minimizer of the restricted regression with $\lambda \leq 768 s
\tilde{\sigma} \sqrt{ \frac{1}{n} \log^2 np}$.
Suppose $n \geq c_1 s \sqrt{sB}$.
Then with probability at least $1-\frac{C}{n}$,
\begin{align}
\|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
&\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 Cnp},
\end{align}
where $c_1$ is an absolute constant and $c, C$ are constants possibly dependent on $b$.
\end{theorem}

@@

A sub-exponential random variable is the square of a sub-Gaussian random
variable \cite{vershynin2010introduction}.
